Data_visualization

### 2018-06-20 Rmd/Data_visualization.Rmd
general changes for data visualization

```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=3}
#load libraries

@@

d<-read.csv("Data/Ovules.csv", sep=";")

colnames(d)[1]<-"C. annuum"
colnames(d)[2]<-"S. lycopersicum"
colnames(d)[3]<-"S. melongera"
colnames(d)[4]<-"P. integrifolia"
colnames(d)[5]<-"B. oleracea"
colnames(d)[6]<-"B. rapa"
colnames(d)[7]<-"E. sativa"
colnames(d)[8]<-"S. alba"

@@

p <- ggplot(d, aes(x = reorder(species, ovules, FUN = median), y = ovules)) +   geom_boxplot()+
labs(title="Ovules per spp.",x="", y = "Ovules")+aes(fill=species)+
theme(plot.title = element_text(hjust = 0.5))

@@

>>>>

```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=4}
#load libraries

@@

d<-read.csv("Data/Ovules.csv", sep=";")
d<- d[,-c(9,11)]
colnames(d)[1]<-"C. annuum"
colnames(d)[2]<-"S. lycopersicum"
colnames(d)[3]<-"S. melongera"
colnames(d)[4]<-"P. integrifolia"
colnames(d)[5]<-"B. oleracea"
colnames(d)[6]<-"B. rapa"
colnames(d)[7]<-"E. sativa"
colnames(d)[8]<-"S. alba"
colnames(d)[9]<-"I. aquatica"
colnames(d)[10]<-"I. purpurea"

@@

p <- ggplot(d, aes(x = reorder(species, ovules, FUN = median), y = ovules)) +   geom_boxplot()+
labs(title="Ovules per spp.",x="", y = "Ovules")+aes(fill=family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
theme(plot.title = element_text(hjust = 0.5))

@@

```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=6}
tab <- read.csv("Data/tab.csv", sep="", header = T)

p <- ggplot(data=tab, aes(x=reorder(species, pollen_ovule_ratio, colour = cut), y=pollen_ovule_ratio))+aes(fill=family)+
  geom_bar(stat="identity", width=0.5)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
  scale_fill_manual(values=colours)
p + ggtitle("Pollen/ovule ratio per species") + theme(plot.title = element_text(hjust = 0.5))+ labs(x = "Species")
